Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
brush up my comment.

\begin{quote}
kazu: the two paragraphs above doe not seem logical to me. I would change these
as follows:

@@

We think that some evidence is useful as user documentation, hence we
want to be able to include it in Haddock comments.  But others are not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.
They should be included in code document. Both kinds of evidence
should be automatically tested.
\end{quote}

\begin{quote}
    sol: remove?
    kazu: yes. But I would add a sentence such as ``This section
    will discuss problems when we try to use these tools for BDD''.

BDD tools should be treat both of them and provide functionality
to extract evidence for users as user documentation.
If we can archive this, BDD tools can be used for
triple purpose: design, documentation and automatic testing.
\end{quote}

>>>>

\begin{quote}
kazu: I'm uncomfortable with the three paragraphs above. I would change these
as follows:

@@

We think that some evidence is useful as user documentation, hence we
want to be able to include it in Haddock comments.  But others are not
useful as user documentation.  E.g. that a particular \texttt{Monoid}
instance is a monoid in the mathematical sense is self-evident.
They should be included in code document. Both kinds of evidence
should be automatically tested.

We propose to use Doctest and Haddock for evidence that is useful as
user documentation, and Hspec for evidence that is not useful as user
documentation. The following subsections disccuss problems when
we try to carry out our proposal of BDD.
\end{quote}
